---
output:
  md_document:
    variant: gfm
---

# statswalesr

<!-- badges: start -->

[![CRAN status](https://www.r-pkg.org/badges/version/statswalesr)](https://cran.r-project.org/package=statswalesr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/jamie-ralph/statswalesr?branch=master&svg=true)](https://ci.appveyor.com/project/jamie-ralph/statswalesr) [![Travis build status](https://travis-ci.org/jamie-ralph/statswalesr.svg?branch=master)](https://travis-ci.org/jamie-ralph/statswalesr)

<!-- badges: end -->

statswalesr is a package for downloading datasets and their associated metadata
from StatsWales. This functionality is limited to datasets that are available 
through the OData feed. You can check this by navigating to your desired 
dataset, scrolling to the bottom, and checking that the "Dataset" link is 
available under the Open Data tab.

## Installation

statswalesr is now on CRAN. To install: 

``` r
install.packages("statswalesr")
```


You can install the development version of statswalesr from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("jamie-ralph/statswalesr")
```
## Example

The code below extracts data about [aircraft movement at Cardiff airport](https://statswales.gov.wales/Catalogue/Transport/Air/aircraftmovementsatcardiffairport-by-movementtype-year) and the associated metadata.

```{r example1, message = FALSE, warning = FALSE, results="hide"}
library(statswalesr)

metadata <- statswalesr::statswales_get_metadata("tran0003")

df <- statswalesr::statswales_get_dataset("tran0003")
```

```{r}

str(df)

```

You can also search for datasets based on key terms. For example, if I wanted
data on farming or agriculture I could do the following:

```{r example2, message = FALSE, warning = FALSE, results="hide"}
library(dplyr)

farming_datasets <- statswales_search(c("farm*", "agri*"))
```

```{r}
glimpse(farming_datasets)
```
